quollr: An R Package for Visualizing $2-\\text{D}$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-08 paper-quollr.Rmd
Updated Link plots arguments

```{r, echo=TRUE, eval=FALSE}
df_exe <- comb_all_data_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  model_highd = scurve_model_obj$model_highd, 
  model_2d = scurve_model_obj$model_2d
  )
```

@@

```{r, echo=TRUE, eval=FALSE}
df_exe <- comb_all_data_model_error(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  model_highd = scurve_model_obj$model_highd, 
  model_2d = scurve_model_obj$model_2d, 
  error_data = model_error)
```

>>>>

```{r, echo=TRUE, eval=FALSE}
df_exe <- comb_all_data_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )
```

@@

```{r, echo=TRUE, eval=FALSE}
df_exe <- comb_all_data_model_error(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids, 
  error_data = model_error
  )
```
